Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-11 main_paper.tex
Spellcheck main paper

Second, if the error terms have pronounced heteroskedasticity, it can be
advantageous to transform the residuals before applying the bootstrap, as
discussed by \citet{DF08} --- these transformations typically do not affect the
first-order asymptotic properties of the bootstrap distribution but can provide
improvements in finite samples analagous to alternative
heteroskedasticity-robust variance estimators. (\citealp{mackinnon1985some}, and
\citealp{mackinnon2013thirty}.) Since RD estimators rely on a small subset of
the data available in any application, these finite-sample adjustments can be
especially effective in improving performance, and we use the ``HC3''
transformation proposed by \citet{DF08} in this paper's Monte Carlo simulations
and empirical exercise.

@@

The column ``CI Coverage'' lists the experimental coverage of each interval.
In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart. In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity. 
The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.

>>>>

Second, if the error terms have pronounced heteroskedasticity, it can be
advantageous to transform the residuals before applying the bootstrap, as
discussed by \citet{DF08} --- these transformations typically do not affect the
first-order asymptotic properties of the bootstrap distribution but can provide
improvements in finite samples analogous to alternative
heteroskedasticity-robust variance estimators. (\citealp{mackinnon1985some}, and
\citealp{mackinnon2013thirty}.) Since RD estimators rely on a small subset of
the data available in any application, these finite-sample adjustments can be
especially effective in improving performance, and we use the ``HC3''
transformation proposed by \citet{DF08} in this paper's Monte Carlo simulations
and empirical exercise.

@@

The column ``CI Coverage'' lists the experimental coverage of each interval.
In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
our proposed bootstrap procedure has coverage about one percentage lower than the CCT's analytical counterpart. In Panel B, the coverage is very similar to Panel A, showing that both procedures are robust to heteroskedasticity.
The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.
